Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-05-09 manuscript/manuscript.tex
stat format

\documentclass[12pt, titlepage, letterpaper]{article}

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{multirow}
\allowdisplaybreaks

\usepackage[]{lineno}
\linenumbers*[1]
% %% patches to make lineno work better with amsmath
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
 \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
 \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
 \renewenvironment{#1}%
 {\linenomath\csname old#1\endcsname}%
 {\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
 \patchAmsMathEnvironmentForLineno{#1}%
 \patchAmsMathEnvironmentForLineno{#1*}}%

\AtBeginDocument{%
 \patchBothAmsMathEnvironmentsForLineno{equation}%
 \patchBothAmsMathEnvironmentsForLineno{align}%
 \patchBothAmsMathEnvironmentsForLineno{flalign}%
 \patchBothAmsMathEnvironmentsForLineno{alignat}%
 \patchBothAmsMathEnvironmentsForLineno{gather}%
 \patchBothAmsMathEnvironmentsForLineno{multline}%
}

% control floats
\renewcommand\floatpagefraction{.9}
\renewcommand\topfraction{.9}
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.1}
\setcounter{totalnumber}{50}
\setcounter{topnumber}{50}
\setcounter{bottomnumber}{50}

@@

\begin{document}
%\maketitle

\title{Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test}
  \author{Mathew Chandy \\
  % \href{mailto:mathew.chandy@uconn.edu}
  % {\nolinkurl{mathew.chandy@uconn.edu}}\\
 Elizabeth Schifano\\
 Jun Yan\\
 Xianyang Zhang
}

@@

\begin{abstract}

The Kolmogorov--Smirnov (KS) test is a widely used statistical test that
assesses the conformity of a sample to a specified distribution. Its efficacy,
however, diminishes with serially dependent data and when parameters
within the hypothesized distribution are unknown. For independent data,
parametric and nonparametric bootstrap procedure are available to adjust for
estimated parameters. For serially dependent stationary data, parametric
bootstrap has been developed with a working serial dependence structure. A
counterpart for the nonparametric bootstrap approach, which needs a bias
correction, has not been studied. Addressing this gap, our study introduces a
bias correction method employing a nonparametric block bootstrap, which
approximates the distribution of the KS statistic accounting for unspecified
serial dependence and unspecified parameters. We assess its effectiveness
through simulations, scrutinizing both its size and power. The practicality of
our method is further illustrated with an examination of stock returns from the 
S\&P 500 index, showcasing its utility in real-world
applications.

\bigskip
\noindent{\sc Keywords}:
bias-correction; 
serial dependence;
time series. 
\end{abstract}

\doublespace

\section{Introduction}
\label{sec:intro}

@@

\section{Methods}
\label{sec:methods}

@@

\subsection{Kolmogorov--Smirnov Test}

@@

\subsection{Nonparametric Bootstrap for Independent Data}

@@

\subsection{Nonparametric Block Bootstrap for Stationary Series}

@@

\section{Simulation Studies}
\label{sec:simu}

@@

\subsection{Size}
To assess the actual size of the test, our strategy is to
generate a large number of stationary time series $X_t$ with a certain marginal
distribution $F(\cdot; \theta)$, and for each time series, use our method to
test if $X_t$ follows a hypothesized marginal distribution $F(\cdot; \theta)$
with some unknown $\theta$. If the test holds its size, the p-value
of the test should be uniformly distributed between 0 and 1. We will validate
method with different marginal distributions to ensure that it is robust.
In order for the method to work, a large number of replicates is necessary.

@@

\section{Conclusion}
\label{sec:conclusion}

@@

\jy{QC bib entries: page numbers missing for some journal articles.}
\mc{couldn't find it for naess2012application}

\bibliographystyle{asa}
\bibliography{citations}

\end{document}
%%% LocalWords: nonparametric semiparametric autocorrelation ARMA
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% ispell-personal-dictionary: ".aspell.en.pws"
%%% fill-column: 80
%%% eval: (auto-fill-mode 1)
%%% End:

>>>>

\documentclass[APA,Times1COL]{WileyNJDv5} %STIX1COL,STIX2COL,STIXSMALL

\usepackage{natbib}

\articletype{Article Type}%

\received{Date Month Year}
\revised{Date Month Year}
\accepted{Date Month Year}
\journal{Journal}
\volume{00}
\copyyear{2023}
\startpage{1}

\raggedbottom

@@

\begin{document}

\title{Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test}

\author[1]{Mathew Chandy}

\author[1]{Elizabeth Schifano}

\author[1]{Jun Yan}

\author[2]{Xianyang Zhang}

\authormark{CHANDY \textsc{et al.}}
\titlemark{NONPARAMETRIC BLOCK BOOTSTRAP KOLMOGOROV-SMIRNOV GOODNESS-OF-FIT TEST}

\address[1]{\orgdiv{Statistics}, \orgname{University of Connecticut},
\orgaddress{\state{Connecticut}, \country{United States}}}

\address[2]{\orgdiv{Statistics}, \orgname{Texas A\&M University}, \orgaddress{\state{Texas}, \country{United States}}}

\corres{\email{mathewchandy03@gmail.com}
\email{elizabeth.schifano@uconn.edu}
\email{jun.yan@uconn.edu} 
\email{zhangxiany@stat.tamu.edu} }

\presentaddress{21 Maxfelix Dr, Storrs, CT 06268}

%\fundingInfo{Text}
%\JELinfo{ejlje}

\abstract[Abstract]{The Kolmogorov--Smirnov (KS) test is a widely used statistical test that
assesses the conformity of a sample to a specified distribution. Its efficacy,
however, diminishes with serially dependent data and when parameters
within the hypothesized distribution are unknown. For independent data,
parametric and nonparametric bootstrap procedure are available to adjust for
estimated parameters. For serially dependent stationary data, parametric
bootstrap has been developed with a working serial dependence structure. A
counterpart for the nonparametric bootstrap approach, which needs a bias
correction, has not been studied. Addressing this gap, our study introduces a
bias correction method employing a nonparametric block bootstrap, which
approximates the distribution of the KS statistic accounting for unspecified
serial dependence and unspecified parameters. We assess its effectiveness
through simulations, scrutinizing both its size and power. The practicality of
our method is further illustrated with an examination of stock returns from the 
S\&P 500 index, showcasing its utility in real-world
applications.}

\keywords{bias-correction, p-value, time series, finance}

\jnlcitation{\cname{%
\author{Chandy M.},
\author{Schifano E},
\author{Yan J}, and
\author{Zhang X}}.
\ctitle{Nonparametric block bootstrap Kolmogorov-Smirnov goodness-of-fit test.} \cjournal{\it Stat.} \cvol{2024;}.}

@@

\renewcommand\thefootnote{}
\footnotetext{\textbf{Abbreviations:} }

\renewcommand\thefootnote{\fnsymbol{footnote}}
\setcounter{footnote}{1}

\section{Introduction}\label{sec:intro}

@@

\section{Methods}\label{sec:methods}

@@

\subsection{Kolmogorov--Smirnov test}

@@

\subsection{Nonparametric bootstrap for independent data}

@@

\subsection{Nonparametric block bootstrap for stationary series}

@@

\section{Simulation Studies}\label{sec:simu}

@@

\subsection{Size}
To assess the actual size of the test, our strategy is to
generate a large number of stationary time series $X_t$ with a certain marginal
distribution $F(\cdot; \theta)$, and for each time series, use our method to
test if $X_t$ follows a hypothesized marginal distribution $F(\cdot; \theta)$
with some unknown $\theta$. If the test holds its size, the p-value
of the test should be uniformly distributed between 0 and 1. We will validate
our method with different marginal distributions to ensure that it is robust.
In order for the method to work, a large number of replicates is necessary.

@@

\section{Conclusions}\label{sec:conclusion}

@@

%\backmatter
\bmsection*{Author contributions}

This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text.

\bmsection*{Acknowledgments}
This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here.

\bmsection*{Data availability statement}

\bmsection*{Funding statement}

None reported.

\bmsection*{Conflict of interest disclosure}

The authors declare no potential conflict of interests.

\bmsection*{Ethics approval statement}

\bibliography{citations}

\bmsection*{Supporting information}

Additional supporting information may be found in the
online version of the article at the publisher’s website.

\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;

\end{document}
